---
title: "summ_sims"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
remove(list = ls())
library(dplyr)
library(ggplot2)
library(ggpubr)
library(gridExtra)
library(latex2exp)

res.beta.strapp <- readRDS(file = '/proj/ibrahimlab/strapp_paper3/R/res_beta_strapp.rds')
beta.strapp     <- res.beta.strapp$beta.strapp
#var_names = c('beta[1]', 'beta[2]', 'beta[3]', 'beta[4]') # covariate names in simres
```


```{r}
# compute posterior probabilities of beta < 0
get_post_prob <- function(n1, a0, sim.dir){
  files   <- list.files(path = sim.dir, pattern = '.rds')
  if (a0 == 0){ # a0 = 0 for the reference prior
    idx     <- grepl(pattern = paste0('_n1_', n1, '_refprior_'), files)
    files   <- files[idx]
  } else{
    idx     <- grepl(pattern = paste0('_n1_', n1, '_a0_', a0), files)
    files   <- files[idx]
  }
  
  post_prob = c()
  for (i in seq_len(length(files))) {
    simres <- readRDS(file.path(sim.dir, files[i]))$simres
    post_prob =c(post_prob,
                 as.numeric(unlist(simres %>% filter(variable == 'beta[1]') %>% select('post_prob')))
    )
  }
  
  return(post_prob)
}

# get mean posterior probability of rejection 
# reject if the posterior probability of beta_trt < 0 is > q, where
# q is the evidence threshold for each data set based on the empirical distribution of the posterior probability under H0
# q = the 97.5th quantile of the empirical sampling distribution of \int Pr(log HR < 0 | D, H0) f(D | H0)
get_rej_prob <- function(n1, a0, sim.dir, q){
  post_prob = get_post_prob(n1, a0, sim.dir)
  return(mean(post_prob > q))
}

get_MSE_trt <- function(beta_true, n1, a0, sim.dir){
  files   <- list.files(path = sim.dir, pattern = '.rds')
  if (a0 == 0){ # a0 = 0 for the reference prior
    idx     <- grepl(pattern = paste0('_n1_', n1, '_refprior_'), files)
    files   <- files[idx]
  } else{
    idx     <- grepl(pattern = paste0('_n1_', n1, '_a0_', a0), files)
    files   <- files[idx]
  }
  
  MSE = c()
  for (i in seq_len(length(files))) {
    simres <- readRDS(file.path(sim.dir, files[i]))$simres
    simres <- simres %>% filter(variable == 'beta[1]') %>% mutate(mse = (post_mean - beta_true[1])^2)
    MSE =c(MSE, as.numeric(unlist(simres %>% select('mse')))
    )
  }
  
  mean(MSE) 
  
}
```


# Obtain the Evidence Threshold

```{r}
# q = the 97.5th quantile of the empirical sampling distribution of \int Pr(log HR < 0 | D, H0) f(D | H0)
n1      <- seq(550, 750, by = 20)
q1_list <- sapply(n1, function(x){
  post_prob = get_post_prob(n1 = x, a0 = 0, sim.dir = '/proj/ibrahimlab/strapp_paper3/Sims/H0/refprior')
  as.numeric(quantile(post_prob, prob = 0.975))
})
names(q1_list) <- paste0('n1 = ', n1)
```



# Obtain Power and MSE for Treatment Effect (under H1)

```{r}
n1 <- seq(550, 750, by = 20)
a0 <- c(0.2, 0.4, 0.6, 0.8)
grid <- expand.grid(
  n1 = n1,
  a0 = a0,
  stringsAsFactors = FALSE
)

sim.dir.strapp    <- '/proj/ibrahimlab/strapp_paper3/Sims/H1/strapp'
sim.dir.genstrapp <- '/proj/ibrahimlab/strapp_paper3/Sims/H1/genstrapp'
sim.dir.pp        <- '/proj/ibrahimlab/strapp_paper3/Sims/H1/power_prior'
sim.dir.ref       <- '/proj/ibrahimlab/strapp_paper3/Sims/H1/refprior'

power.strapp      <- apply(grid, 1, function(r){get_rej_prob(n1 = r[1], a0 = r[2], sim.dir = sim.dir.strapp, q = q1_list[paste0('n1 = ', r[1])])})
mse.strapp        <- apply(grid, 1, function(r){get_MSE_trt(beta_true = beta.strapp, n1 = r[1], a0 = r[2], sim.dir = sim.dir.strapp)})     
grid.strapp       <- grid
grid.strapp$power <- power.strapp
grid.strapp$mse   <- mse.strapp
grid.strapp$prior <- 'straPP'

power.genstrapp      <- apply(grid, 1, function(r){get_rej_prob(n1 = r[1], a0 = r[2], sim.dir = sim.dir.genstrapp, q = q1_list[paste0('n1 = ', r[1])])})
mse.genstrapp        <- apply(grid, 1, function(r){get_MSE_trt(beta_true = beta.strapp, n1 = r[1], a0 = r[2], sim.dir = sim.dir.genstrapp)})     
grid.genstrapp       <- grid
grid.genstrapp$power <- power.genstrapp
grid.genstrapp$mse   <- mse.genstrapp
grid.genstrapp$prior <- 'Gen-straPP'

power.pp      <- apply(grid, 1, function(r){get_rej_prob(n1 = r[1], a0 = r[2], sim.dir = sim.dir.pp, q = q1_list[paste0('n1 = ', r[1])])})
mse.pp        <- apply(grid, 1, function(r){get_MSE_trt(beta_true = beta.strapp, n1 = r[1], a0 = r[2], sim.dir = sim.dir.pp)})
grid.pp       <- grid
grid.pp$power <- power.pp
grid.pp$mse   <- mse.pp
grid.pp$prior <- 'PP'

power.ref      <- apply(grid, 1, function(r){get_rej_prob(n1 = r[1], a0 = 0, sim.dir = sim.dir.ref, q = q1_list[paste0('n1 = ', r[1])])})
mse.ref        <- apply(grid, 1, function(r){get_MSE_trt(beta_true = beta.strapp, n1 = r[1], a0 = 0, sim.dir = sim.dir.ref)})
grid.ref       <- grid
grid.ref$power <- power.ref
grid.ref$mse   <- mse.ref
grid.ref$prior <- 'Reference'

df.power <- rbind(grid.strapp, grid.genstrapp, grid.pp, grid.ref)

avg_events_per_n1 <- readRDS("/proj/ibrahimlab/strapp_paper3/R/avg_events_per_n1_H1.rds")
avg_events_per_n1 <- round(avg_events_per_n1)

# ae = avg_events
for(i in 1:nrow(df.power)){
  df.power$x_label[i] <- paste0('n = ', df.power$n1[i], '\nae = ', avg_events_per_n1[which(n1 == df.power$n1[i])])
}
```


# Obtain Type I Error and MSE for Treatment Effect (under H0)

```{r}
n1 <- seq(550, 750, by = 20)
a0 <- c(0.2, 0.4, 0.6, 0.8)
grid <- expand.grid(
  n1 = n1,
  a0 = a0,
  stringsAsFactors = FALSE
)

sim.dir.strapp    <- '/proj/ibrahimlab/strapp_paper3/Sims/H0/strapp'
sim.dir.genstrapp <- '/proj/ibrahimlab/strapp_paper3/Sims/H0/genstrapp'
sim.dir.pp        <- '/proj/ibrahimlab/strapp_paper3/Sims/H0/power_prior'
sim.dir.ref       <- '/proj/ibrahimlab/strapp_paper3/Sims/H0/refprior'

beta.strapp.null    <- beta.strapp
beta.strapp.null[1] <- 0

alpha.strapp             <- apply(grid, 1, function(r){get_rej_prob(n1 = r[1], a0 = r[2], sim.dir = sim.dir.strapp, q = q1_list[paste0('n1 = ', r[1])])})
mse.strapp               <- apply(grid, 1, function(r){get_MSE_trt(beta_true = beta.strapp.null, n1 = r[1], a0 = r[2], sim.dir = sim.dir.strapp)})
grid.strapp              <- grid
grid.strapp$type_I_error <- alpha.strapp
grid.strapp$mse          <- mse.strapp
grid.strapp$prior        <- 'straPP'

alpha.genstrapp             <- apply(grid, 1, function(r){get_rej_prob(n1 = r[1], a0 = r[2], sim.dir = sim.dir.genstrapp, q = q1_list[paste0('n1 = ', r[1])])})
mse.genstrapp               <- apply(grid, 1, function(r){get_MSE_trt(beta_true = beta.strapp.null, n1 = r[1], a0 = r[2], sim.dir = sim.dir.genstrapp)})     
grid.genstrapp              <- grid
grid.genstrapp$type_I_error <- alpha.genstrapp
grid.genstrapp$mse          <- mse.genstrapp
grid.genstrapp$prior        <- 'Gen-straPP'

alpha.pp             <- apply(grid, 1, function(r){get_rej_prob(n1 = r[1], a0 = r[2], sim.dir = sim.dir.pp, q = q1_list[paste0('n1 = ', r[1])])})
mse.pp               <- apply(grid, 1, function(r){get_MSE_trt(beta_true = beta.strapp.null, n1 = r[1], a0 = r[2], sim.dir = sim.dir.pp)})
grid.pp              <- grid
grid.pp$type_I_error <- alpha.pp
grid.pp$mse          <- mse.pp
grid.pp$prior        <- 'PP'

alpha.ref             <- apply(grid, 1, function(r){get_rej_prob(n1 = r[1], a0 = 0, sim.dir = sim.dir.ref, q = q1_list[paste0('n1 = ', r[1])])})
mse.ref               <- apply(grid, 1, function(r){get_MSE_trt(beta_true = beta.strapp.null, n1 = r[1], a0 = 0, sim.dir = sim.dir.ref)})
grid.ref              <- grid
grid.ref$type_I_error <- alpha.ref
grid.ref$mse          <- mse.ref
grid.ref$prior        <- 'Reference'

df.typeIerr <- rbind(grid.strapp, grid.genstrapp, grid.pp, grid.ref)

avg_events_per_n1 <- readRDS("/proj/ibrahimlab/strapp_paper3/R/avg_events_per_n1_H0.rds")
avg_events_per_n1 <- round(avg_events_per_n1)

# ae = avg_events
for(i in 1:nrow(df.typeIerr)){
  df.typeIerr$x_label[i] <- paste0('n = ', df.typeIerr$n1[i], '\nae = ', avg_events_per_n1[which(n1 == df.typeIerr$n1[i])])
}
```


# Some Plots/Tables

## Plots by a0

```{r}
plt_power_by_a0 <- function(df, a0_val){
  df %>% 
    filter(a0 == a0_val) %>%
    ggplot(aes(x = n1, y = power, linetype = prior, shape = prior, color = prior)) +
    ylim(0.4, 1) +
    labs(y = "power", x = "", subtitle = paste0('a0 = ', a0_val)) +
    geom_point() +
    geom_smooth(se = FALSE) +
    scale_x_continuous(breaks = df.power$n1, labels = df.power$x_label)
}

plt_typeIerr_by_a0 <- function(df, a0_val){
  df %>% 
    filter(a0 == a0_val) %>%
    ggplot(aes(x = n1, y = type_I_error, linetype = prior, shape = prior, color = prior)) +
    ylim(0, 0.2)  +
    labs(y = "type I error", x = "", subtitle = paste0('a0 = ', a0_val)) +
    geom_point() +
    geom_smooth(se = FALSE) +
    scale_x_continuous(breaks = df.power$n1, labels = df.power$x_label)
}

# hypothesis = 'Null' or 'Alternative'
plt_mse_by_a0 <- function(df, a0_val, hypothesis){
  df %>% 
    filter(a0 == a0_val) %>%
    ggplot(aes(x = n1, y = mse, linetype = prior, shape = prior, color = prior)) +
    ylim(0, 0.05) +
    labs(y = "MSE", x = "", subtitle = paste0('a0 = ', a0_val, ', under the ', hypothesis)) +
    geom_point() +
    geom_smooth(se = FALSE) +
    scale_x_continuous(breaks = df.power$n1, labels = df.power$x_label)
}
```


## Create combined plots of power and type I error

```{r}
# create combined plots of power and type I error
p11 = df.power %>% 
  filter(a0 == 0.2) %>%
  ggplot(aes(x = n1, y = power, linetype = prior, shape = prior, color = prior)) +
  ylim(0.4, 1) +
  labs(y = "", x = "(a)"
       , tag = TeX("$a_0 = 0.2$")
       #, subtitle = "Power"
       ) +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.power$n1, labels = df.power$x_label) +
  theme(legend.position = "none"
        , plot.tag = element_text(angle = 90, size = 12)
        , plot.tag.position = "left"
        #, plot.subtitle=element_text(hjust=0.5, size = 12)
        )

p21 = df.power %>% 
  filter(a0 == 0.4) %>%
  ggplot(aes(x = n1, y = power, linetype = prior, shape = prior, color = prior)) +
  ylim(0.4, 1) +
  labs(y = "", x = "(b)"
       , tag = TeX("$a_0 = 0.4$")) +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.power$n1, labels = df.power$x_label) +
  theme(legend.position = "none"
        , plot.tag = element_text(angle = 90, size = 12)
        , plot.tag.position = "left")

p31 = df.power %>% 
  filter(a0 == 0.6) %>%
  ggplot(aes(x = n1, y = power, linetype = prior, shape = prior, color = prior)) +
  ylim(0.4, 1) +
  labs(y = "", x = "(c)"
       , tag = TeX("$a_0 = 0.6$")) +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.power$n1, labels = df.power$x_label) +
  theme(legend.position = "none"
        , plot.tag = element_text(angle = 90, size = 12)
        , plot.tag.position = "left")

p41 = df.power %>% 
  filter(a0 == 0.8) %>%
  ggplot(aes(x = n1, y = power, linetype = prior, shape = prior, color = prior)) +
  ylim(0.4, 1) +
  labs(y = "", x = "(d)"
       , tag = TeX("$a_0 = 0.8$")) +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.power$n1, labels = df.power$x_label) +
  theme(legend.position = "none"
        , plot.tag = element_text(angle = 90, size = 12)
        , plot.tag.position = "left")

p12 = df.typeIerr %>% 
  filter(a0 == 0.2) %>%
  ggplot(aes(x = n1, y = type_I_error, linetype = prior, shape = prior, color = prior)) +
  ylim(0, 0.2)  +
  labs(y = "", x = "(e)") +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.typeIerr$n1, labels = df.typeIerr$x_label) +
  theme(legend.position = "none")

p22 = df.typeIerr %>% 
  filter(a0 == 0.4) %>%
  ggplot(aes(x = n1, y = type_I_error, linetype = prior, shape = prior, color = prior)) +
  ylim(0, 0.2)  +
  labs(y = "", x = "(f)") +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.typeIerr$n1, labels = df.typeIerr$x_label) +
  theme(legend.position = "none")
  
p32 = df.typeIerr %>% 
  filter(a0 == 0.6) %>%
  ggplot(aes(x = n1, y = type_I_error, linetype = prior, shape = prior, color = prior)) +
  ylim(0, 0.2)  +
  labs(y = "", x = "(g)") +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.typeIerr$n1, labels = df.typeIerr$x_label) +
  theme(legend.position = "none")

p42 = df.typeIerr %>% 
  filter(a0 == 0.8) %>%
  ggplot(aes(x = n1, y = type_I_error, linetype = prior, shape = prior, color = prior)) +
  ylim(0, 0.2)  +
  labs(y = "", x = "(h)") +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.typeIerr$n1, labels = df.typeIerr$x_label) +
  theme(legend.position = "none")

#ggarrange(
#  ggarrange(p11, p12, ncol = 2, labels = c("a0 = 0.2", "")), # First row with line plot
  # Second row
#  ggarrange(p21, p22, ncol = 2, labels = c("a0 = 0.4", ""),
#            common.legend = TRUE, legend = "bottom"), 
#  nrow = 2
#) 

pl = list(p11, p21, p31, p41, p12, p22, p32, p42)

# Create row and column titles
col.titles = c("Power", "Type I Error Rate")
#row.titles = paste0('a0 = ', c(0.2, 0.4, 0.6, 0.8))

# Add row titles
#pl[1:4] = lapply(1:4, function(i) arrangeGrob(pl[[i]], 
#                                              left=row.titles[i]
                                              #left = text_grob(row.titles[i], size = 10, face = "bold")
#)
#)

# function to extract legend from plot
get_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}

# p11 with legend
p11_legend <- df.power %>% 
  filter(a0 == 0.2) %>%
  ggplot(aes(x = n1, y = power, linetype = prior, shape = prior, color = prior)) +
  ylim(0.4, 1) +
  labs(y = "", x = "(a)") +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.power$n1, labels = df.power$x_label) +
  theme(legend.position = "bottom", legend.text=element_text(size=10),
        legend.key.width= unit(2, 'cm'))

# extract legend from plot1 using above function
legend <- get_legend(p11_legend) 

plts = grid.arrange(grobs = lapply(c(1, 5), function(i) {
  arrangeGrob(grobs=pl[i:(i+3)], 
              top=col.titles[i/4 + 1],
              #top=text_grob(col.titles[i/4 + 1], size = 10, face = "bold"),
              ncol=1)
}), bottom = legend, ncol=2)
annotate_figure(plts, top = text_grob(TeX("Power and Type I Error Rate for Various $(a_0, n)$", bold = T), 
               face = "bold", size = 14))
#width: 1250, height: 850
```



```{r}
p11 = plt_power_by_a0(df.power, 0.2)
p12 = plt_typeIerr_by_a0(df.typeIerr, 0.2)
p21 = plt_power_by_a0(df.power, 0.4)
p22 = plt_typeIerr_by_a0(df.typeIerr, 0.4)
p31 = plt_power_by_a0(df.power, 0.6)
p32 = plt_typeIerr_by_a0(df.typeIerr, 0.6)
p41 = plt_power_by_a0(df.power, 0.8)
p42 = plt_typeIerr_by_a0(df.typeIerr, 0.8)

plts = ggarrange(p11, p12, p21, p22, p31, p32, p41, p42, 
          ncol = 2,nrow = 2,
          common.legend = TRUE, legend = "bottom")

plts[[1]]
plts[[2]]

```


```{r}
p11_2 = plt_mse_by_a0(df.power, 0.2, 'Null')
p12_2 = plt_mse_by_a0(df.typeIerr, 0.2, 'Alternative')
p21_2 = plt_mse_by_a0(df.power, 0.4, 'Null')
p22_2 = plt_mse_by_a0(df.typeIerr, 0.4, 'Alternative')
p31_2 = plt_mse_by_a0(df.power, 0.6, 'Null')
p32_2 = plt_mse_by_a0(df.typeIerr, 0.6, 'Alternative')
p41_2 = plt_mse_by_a0(df.power, 0.8, 'Null')
p42_2 = plt_mse_by_a0(df.typeIerr, 0.8, 'Alternative')

plts_mse = ggarrange(p11_2, p12_2, p21_2, p22_2, p31_2, p32_2, p41_2, p42_2, 
          ncol = 2,nrow = 2,
          common.legend = TRUE, legend = "bottom")
plts_mse[[1]]
plts_mse[[2]]
```

## Create combined plots for MSE

```{r}
p11 = df.power %>% 
  filter(a0 == 0.2) %>%
  ggplot(aes(x = n1, y = mse, linetype = prior, shape = prior, color = prior)) +
  ylim(0, 0.05) +
  labs(y = "", x = "(a)"
       , tag = TeX("$a_0 = 0.2$")
       , subtitle = TeX("MSE under $\\pi_{1}^{(s)}$")) +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.power$n1, labels = df.power$x_label) +
  theme(legend.position = "none"
        , plot.tag = element_text(angle = 90, size = 12)
        , plot.tag.position = "left"
        , plot.subtitle=element_text(hjust=0.5, size = 12)
        )

p21 = df.power %>% 
  filter(a0 == 0.4) %>%
  ggplot(aes(x = n1, y = mse, linetype = prior, shape = prior, color = prior)) +
  ylim(0, 0.05) +
  labs(y = "", x = "(b)"
       , tag = TeX("$a_0 = 0.4$")) +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.power$n1, labels = df.power$x_label) +
  theme(legend.position = "none"
        , plot.tag = element_text(angle = 90, size = 12)
        , plot.tag.position = "left")

p31 = df.power %>% 
  filter(a0 == 0.6) %>%
  ggplot(aes(x = n1, y = mse, linetype = prior, shape = prior, color = prior)) +
  ylim(0, 0.05) +
  labs(y = "", x = "(c)"
       , tag = TeX("$a_0 = 0.6$")) +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.power$n1, labels = df.power$x_label) +
  theme(legend.position = "none"
        , plot.tag = element_text(angle = 90, size = 12)
        , plot.tag.position = "left")

p41 = df.power %>% 
  filter(a0 == 0.8) %>%
  ggplot(aes(x = n1, y = mse, linetype = prior, shape = prior, color = prior)) +
  ylim(0, 0.05) +
  labs(y = "", x = "(d)"
       , tag = TeX("$a_0 = 0.8$")) +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.power$n1, labels = df.power$x_label) +
  theme(legend.position = "none"
        , plot.tag = element_text(angle = 90, size = 12)
        , plot.tag.position = "left")

p12 = df.typeIerr %>% 
  filter(a0 == 0.2) %>%
  ggplot(aes(x = n1, y = mse, linetype = prior, shape = prior, color = prior)) +
  ylim(0, 0.05) +
  labs(y = "", x = "(e)"
       , subtitle = TeX("MSE under $\\pi_{0}^{(s)}$")
       ) +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.typeIerr$n1, labels = df.typeIerr$x_label) +
  theme(legend.position = "none"
        , plot.subtitle=element_text(hjust=0.5, size = 12)
        )

p22 = df.typeIerr %>% 
  filter(a0 == 0.4) %>%
  ggplot(aes(x = n1, y = mse, linetype = prior, shape = prior, color = prior)) +
  ylim(0, 0.05) +
  labs(y = "", x = "(f)") +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.typeIerr$n1, labels = df.typeIerr$x_label) +
  theme(legend.position = "none")
  
p32 = df.typeIerr %>% 
  filter(a0 == 0.6) %>%
  ggplot(aes(x = n1, y = mse, linetype = prior, shape = prior, color = prior)) +
  ylim(0, 0.05) +
  labs(y = "", x = "(g)") +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.typeIerr$n1, labels = df.typeIerr$x_label) +
  theme(legend.position = "none")

p42 = df.typeIerr %>% 
  filter(a0 == 0.8) %>%
  ggplot(aes(x = n1, y = mse, linetype = prior, shape = prior, color = prior)) +
  ylim(0, 0.05) +
  labs(y = "", x = "(h)") +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.typeIerr$n1, labels = df.typeIerr$x_label) +
  theme(legend.position = "none")

pl = list(p11, p21, p31, p41, p12, p22, p32, p42)

# Create row and column titles
#col.titles = c("MSE under the Alternative", "MSE under the Null")
#row.titles = paste0('a0 = ', c(0.2, 0.4, 0.6, 0.8))

# Add row titles
#pl[1:4] = lapply(1:4, function(i) arrangeGrob(pl[[i]], 
#                                              left=row.titles[i]
                                              #left = text_grob(row.titles[i], size = 10, face = "bold")
#)
#)

# function to extract legend from plot
get_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}

# p11 with legend
p11_legend <- df.power %>% 
  filter(a0 == 0.2) %>%
  ggplot(aes(x = n1, y = mse, linetype = prior, shape = prior, color = prior)) +
  ylim(0, 0.05) +
  labs(y = "", x = "(a)") +
  geom_point() +
  geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = df.power$n1, labels = df.power$x_label) +
  theme(legend.position = "bottom", legend.text=element_text(size=10),
        legend.key.width= unit(2, 'cm'))

# extract legend from plot1 using above function
legend <- get_legend(p11_legend) 

plts = grid.arrange(grobs = lapply(c(1, 5), function(i) {
  arrangeGrob(grobs=pl[i:(i+3)], 
#              top=col.titles[i/4 + 1],
              #top=text_grob(col.titles[i/4 + 1], size = 10, face = "bold"),
              ncol=1)
}), bottom = legend, ncol=2)
annotate_figure(plts, top = text_grob("MSE under Null and Alternative Sampling Prior", 
               face = "bold", size = 14))
#width: 1250, height: 850
```



# Check Type I Error 

## Case 1

Simulation scenario: implementing reference prior for n1 = 550, number of MCMC sampls = 50000, under H0

```{r}
sim.dir.list <- c('/proj/ibrahimlab/strapp_paper3/Sims/check_type_I_err_refprior/n1_550_nMCMC_25000', '/proj/ibrahimlab/strapp_paper3/Sims/check_type_I_err_refprior/n1_550_nMCMC_50000', '/proj/ibrahimlab/strapp_paper3/Sims/check_type_I_err_refprior/n1_550_nMCMC_75000', '/proj/ibrahimlab/strapp_paper3/Sims/check_type_I_err_refprior/n1_550_nMCMC_100000')

typeIerr_n1_550 <- sapply(sim.dir.list, get_rej_prob, n1 = 550, a0 = 0)
typeIerr_n1_550 
```


## Case 2

Simulation scenario: implementing reference prior for n1 = 2000, number of MCMC sampls = 25000, under H0

```{r}
sim.dir.list2 <- c('/proj/ibrahimlab/strapp_paper3/Sims/check_type_I_err_refprior/n1_2000_nMCMC_25000', '/proj/ibrahimlab/strapp_paper3/Sims/check_type_I_err_refprior/n1_2000_nMCMC_50000', '/proj/ibrahimlab/strapp_paper3/Sims/check_type_I_err_refprior/n1_2000_nMCMC_75000', '/proj/ibrahimlab/strapp_paper3/Sims/check_type_I_err_refprior/n1_2000_nMCMC_100000')
typeIerr_n1_2000 <- sapply(sim.dir.list2, get_rej_prob, n1 = 2000, a0 = 0)
typeIerr_n1_2000 
```

Summary Table of Case 1 and Case 2

```{r}
tab <- cbind(round(as.numeric(typeIerr_n1_550), 4), round(as.numeric(typeIerr_n1_2000), 4))
colnames(tab) <- c('n1 = 550', 'n1 = 2000')
rownames(tab) <- paste0('nMCMC = ', c(25000, 50000, 75000, 100000))

kableExtra::kable(tab)
```


# Histogram of Posterior Probabilities for n1 = 550, 2000

```{r}
get_post_prob_ref <- function(sim.dir, n1){
  files   <- list.files(path = sim.dir, pattern = '.rds')
  idx     <- grepl(pattern = paste0('_n1_', n1, '_refprior_'), files)
  files   <- files[idx]
  
  post_prob = c()
  for (i in seq_len(length(files))) {
    simres <- readRDS(file.path(sim.dir, files[i]))$simres
    post_prob =c(post_prob,
                 as.numeric(unlist(simres %>% filter(variable == 'beta[1]') %>% select('post_prob')))
    )
  }
  
  return(post_prob)
}

#sim.dir1 <- '/pine/scr/x/i/xinxinc/strapp_paper3/sims_test/refprior/check_type_I_err/n1_2000_nMCMC_50000'

sim.dir1 <- '/proj/ibrahimlab/strapp_paper3/Sims/check_type_I_err_refprior/n1_550_nMCMC_25000'
sim.dir2 <- '/proj/ibrahimlab/strapp_paper3/Sims/check_type_I_err_refprior/n1_2000_nMCMC_25000'

post_prob_n1_2000 <- get_post_prob_ref(sim.dir2, n1 = 2000)
post_prob_n1_550 <- get_post_prob_ref(sim.dir1, n1 = 550)

df <- data.frame('post_prob' = c(post_prob_n1_550, post_prob_n1_2000), 'n1' = rep(c('n1 = 550', 'n1 = 2000'), each = 10000))

plt_2000_550 = ggplot(df, aes(x=post_prob)) + 
  labs(x = 'posterior probability under the null', subtitle = 'For Model with All the Covariates')+
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, color = 'red') +
  #facet_grid(n1 ~ .)
  facet_grid(~n1)

plt_2000_550
```

# Histogram of Number of Events for All Covariates

```{r}
remove(list = ls())
library(dplyr)
library(ggplot2)
library(ggpubr)

## source wrappers
wrapper.dir <- '/proj/ibrahimlab/strapp_paper3/R'
source(file.path(wrapper.dir, 'wrappers.R'))

seeds_list <- readRDS(file = '/proj/ibrahimlab/strapp_paper3/R/seeds_list.rds')

res.beta.strapp <- readRDS(file = '/proj/ibrahimlab/strapp_paper3/R/res_beta_strapp.rds')
beta.strapp     <- res.beta.strapp$beta.strapp
X0              <- res.beta.strapp$X0
p_cured         <- res.beta.strapp$p_cured
rm(res.beta.strapp)

get_num_events <- function(n1){
  num_events = vector(length = length(seeds_list))
  
  for (i in seq_len(length(seeds_list))) {
    set.seed(seeds_list[i]) # set seed for generating current data
    ## Take bootstrap samples from the historical data matrix
    X.sim       <- X0[sample(1:nrow(X0), n1, replace = TRUE), ]
    curdata.sim <- rcureexp(pcure = p_cured, X = X.sim, beta = beta.strapp)
    num_events[i] <- sum(curdata.sim$rfscens)
  }
  num_events
}

n1.list    <- c(2000, 5000, 10000, 12000)
num_events <- lapply(n1.list, get_num_events)
df <- data.frame(num_events = unlist(num_events),  n1 = rep(n1.list, each = 10000))

plot_hist_events <- function(n1_val, df = df){
  p = ggplot(df %>% filter(n1 == n1_val), aes(x=num_events)) + 
  labs(x = paste0('number of events for n1 = ', n1_val))+
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, color = 'red') 
  p
}

plts = lapply(n1.list, plot_hist_events, df = df)
plts_covar = ggarrange(plts[[1]], plts[[2]], plts[[3]], plts[[4]], nrow = 2, ncol = 2)
annotate_figure(plts_covar, top = text_grob("Histogram of Number of Events for Model Including All Covariates", 
               face = "bold", size = 14))

```


# Histogram of Number of Events for Treatment-Only Model

```{r}
remove(list = ls())
library(dplyr)
library(ggplot2)
library(ggpubr)

## source wrappers
wrapper.dir <- '/proj/ibrahimlab/strapp_paper3/R'
source(file.path(wrapper.dir, 'wrappers.R'))

seeds_list <- readRDS(file = '/proj/ibrahimlab/strapp_paper3/R/seeds_list.rds')

res.beta.strapp <- readRDS(file = '/proj/ibrahimlab/strapp_paper3/R/res_beta_strapp.rds')
beta.strapp <- 0
beta.strapp <- as.matrix(beta.strapp)
X0          <- res.beta.strapp$X0
X0          <- X0[, 1, drop = F]
p_cured     <- res.beta.strapp$p_cured
rm(res.beta.strapp)

get_num_events <- function(n1){
  num_events = vector(length = length(seeds_list))
  
  for (i in seq_len(length(seeds_list))) {
    set.seed(seeds_list[i]) # set seed for generating current data
    ## Take bootstrap samples from the historical data matrix
    X.sim       <- X0[sample(1:nrow(X0), n1, replace = TRUE), , drop = F]
    curdata.sim <- rcureexp(pcure = p_cured, X = X.sim, beta = beta.strapp)
    num_events[i] <- sum(curdata.sim$rfscens)
  }
  num_events
}

n1.list    <- c(2000, 5000, 10000, 12000)
num_events <- lapply(n1.list, get_num_events)
df <- data.frame(num_events = unlist(num_events),  n1 = rep(n1.list, each = 10000))

plot_hist_events <- function(n1_val, df = df){
  p = ggplot(df %>% filter(n1 == n1_val), aes(x=num_events)) + 
  labs(x = paste0('number of events for n1 = ', n1_val))+
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, color = 'red') 
  p
}

plts = lapply(n1.list, plot_hist_events, df = df)
plts_trt_only = ggarrange(plts[[1]], plts[[2]], plts[[3]], plts[[4]], nrow = 2, ncol = 2)
annotate_figure(plts_trt_only, top = text_grob("Histogram of Number of Events for Treatment-Only Model", 
               face = "bold", size = 14))

n1.list    <- c(10000, 500)
num_events <- lapply(n1.list, get_num_events)
mean(num_events[[1]]) # 3970.295
mean(num_events[[2]]) # 198.4029
```


# Histogram of posterior probabilities for n1 = 10000 and 500, treatment-only model

```{r}
# plot histogram of posterior probabilities for n1 = 10000 under H0, refprior
library(dplyr)
library(latex2exp)
library(ggplot2)
library(ggpubr)

get_rej_prob <- function(sim.dir){
  files   <- list.files(path = sim.dir, pattern = '.rds')
  post_prob = c()
  for (i in seq_len(length(files))) {
    simres <- readRDS(file.path(sim.dir, files[i]))$simres
    post_prob =c(post_prob,
                 as.numeric(unlist(simres %>% filter(variable == 'beta[1]') %>% select('post_prob')))
    )
  }
  
  return(post_prob)
}

sim.dir1 <- '/proj/ibrahimlab/strapp_paper3/Sims/check_type_I_err_refprior/n1_10000_nMCMC_25000_trt_only'
sim.dir2 <- '/work/users/x/i/xinxinc/strapp_paper3/check_typeIerr/n1_500_trt_only'

post_prob_n1_10000 <- get_rej_prob(sim.dir = sim.dir1)
post_prob_n1_500   <- get_rej_prob(sim.dir = sim.dir2)

df <- data.frame('post_prob' = c(post_prob_n1_10000, post_prob_n1_500), 'n' = rep(c('n = 10,000', 'n = 500'), each = 10000))
df$n <- factor(df$n, levels = c('n = 500', 'n = 10,000'))

plt_500_10000 = ggplot(df, aes(x=post_prob)) + 
  labs(x = TeX("Posterior probability under $\\pi_0^{(s)}$"), subtitle = 'For Treatment-Only Model')+
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, color = 'red') +
  #facet_grid(n1 ~ .)
  facet_grid(~n) + 
  theme(plot.subtitle=element_text(hjust=0.5))
annotate_figure(plt_500_10000, top = text_grob("Histograms of Posterior Probability under Null Sampling Prior", 
                                               face = "bold", size = 14)
)
#width: 1200, height: 480

#sim.dir <- '/pine/scr/x/i/xinxinc/strapp_paper3/sims_test/refprior/check_type_I_err/n1_10000_nMCMC_25000_trt_only'
sim.dir <- '/proj/ibrahimlab/strapp_paper3/Sims/check_type_I_err_refprior/n1_10000_nMCMC_25000_trt_only'
post_prob <- get_rej_prob(sim.dir = sim.dir)
mean(post_prob > (1 - 0.025)) # 0.0299

library(ggplot2)
df <- data.frame('post_prob' = post_prob, n1 = 'n1 = 10000')

plt_10000 = ggplot(df, aes(x=post_prob)) + 
  labs(x = 'posterior probability under the null', subtitle = 'For Treatment-Only Model')+
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, color = 'red')+
  facet_grid(~n1)

plt_2000_550

plt = ggarrange(plt_2000_550, plt_10000, nrow = 2, labels = c("(a)", "(b)"))
plt
```

